The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Add scoring information.

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{booktabs}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}
\usepackage{xspace}

@@

Since there are vast differences in size
between benchmark families in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
\maintrack benchmark in order to de-emphasize large benchmark
families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
log scaling seems a reasonable compromise between linearly combining
numbers of benchmarks, which would overemphasize large families, and
simply averaging the fraction of benchmarks solved, which would
overemphasize small families.

>>>>

\usepackage{jsat}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{booktabs}
%\usepackage[pdf]{pstricks}
%\usepackage{pst-tree}
\usepackage{xspace}
\usepackage{enumitem}

@@

The \emph{raw benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
\end{itemize}
\noindent
For the \maintrack and \apptrack,
$N$ is defined as the number of {\tt check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.

This raw score corresponds to the \emph{raw parallel score} (all values are
determined for solver performance within the wall-clock time limit).  To
evaluate sequential performance, we derive a \emph{raw sequential score} by
imposing a (virtual) CPU time limit equal to the wall-clock time limit~$T$.  A
solver result is taken into consideration for the sequential score only if the
solver process terminates within this CPU time limit.

Until 2015, the competition used these raw scores for all tracks to determine
the division score of a solver as the sum of the scores of all benchmarks in
that division.
Fewer errors in a division takes precedence over more correct solutions
(resp.~reduction), which takes precedence over less wall-clock time taken,
which takes precedence over less CPU time taken.
However, since there are vast differences in size between benchmark families in
the SMT Library, the competition since~2016 uses a scoring method that assigns
a weight to each benchmark in the \maintrack and \ucoretrack in order to
de-emphasize large benchmark families~\cite{rules16,rules17,rules18}.
For application track divisions, division scores were still based on raw scores
only, since application track benchmarks may be partially solved. Defining a
useful sequential score for the application track would require information not
provided by the raw score, e.g., detailed timing information for each result.

\paragraph{Benchmark Weights (\maintrack and \ucoretrack 2016-2018).} The \emph{weight} of a
benchmark in the main track is computed as $\alpha = (1 + \ln F)/F$,
where~$F\geq 1$ is the size of the benchmark's family.  We then define its
\emph{normalized weight} as $\alpha' = \alpha / (\sum_{i\in F} \alpha_i)$,
where the sum is over all benchmarks in the division.  The log scaling seems a
reasonable compromise between linearly combining numbers of benchmarks, which
would overemphasize large families, and simply averaging the fraction of
benchmarks solved, which would overemphasize small families.

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
F} \alpha'_i \cdot \langle e \cdot N, n \cdot N, w, c\rangle$$ where the sum is
over all benchmarks in the division to assess parallel performance, and the
weighted sum of all sequential scores to assess sequential performance.
